\name: Combining Bottom-up and top-down approaches through graph learning over interaction networks for drug-target-interaction prediction

### 2021-03-23 paper/main.tex
Added BioSnap integration to preprocessing and predictor

	\begin{tabular}{|l|p{1cm}|p{1cm}|p{1cm}|p{1cm}|}
		\hline
		(c) Approach&\multicolumn{2}{c|}{Original scheme}&\multicolumn{2}{c|}{Protein split}\\
		&Splitting scheme&Macro AUC&Macro AUC&Micro $AUC_p$\\
		\hline
		Naive predictor&DP pairs&$0.85$& --&--\\
		DTINet&DP pairs&$0.91$&$0.74$&$0.67$\\
		DTIGEMS+&DP pairs&$\mathbf{0.93}$& $0.72$& $0.68$ \\
		DTI-CDF&Proteins&$0.85$&$\mathbf{0.85}$&$0.79$\\
		\name&Proteins&$0.84$&$0.84$&$\mathbf{0.84}$\\
		\hline
		\hline
		(d) Approach&\multicolumn{2}{c|}{Original scheme}&\multicolumn{2}{c|}{Protein split}\\
		&Splitting scheme&Macro AUC&Macro AUC&Micro $AUC_p$\\
		\hline
		DeepDTI&Drugs&$0.88$&$0.76$&$0.70$\\
		DeepDTA&DP pairs&$0.88$&$0.77$&$0.69$\\
		DeepConv-DTI&DP pairs&$0.88$&$0.76$&$0.73$\\
		MolTrans&DP pairs&$0.90$&$0.77$&$0.74$\\
		\hline
	\end{tabular}\\

@@

>>>>

	\begin{tabular}{|l|p{1cm}|p{1cm}|p{1cm}|p{1cm}|}
		\hline
		(c) Approach&\multicolumn{2}{c|}{Original scheme}&\multicolumn{2}{c|}{Protein split}\\
		&Splitting scheme&Macro AUC&Macro AUC&Micro $AUC_p$\\
		\hline
		Naive predictor&DP pairs&$0.85$& --&--\\
		DTINet&DP pairs&$0.91$&$0.74$&$0.67$\\
		DTIGEMS+&DP pairs&$\mathbf{0.93}$& $0.72$& $0.68$ \\
		DTI-CDF&Proteins&$0.85$&$\mathbf{0.85}$&$0.79$\\
		\name&Proteins&$0.84$&$0.84$&$\mathbf{0.84}$\\
		\hline
		\hline
		(d) Approach&\multicolumn{2}{c|}{Original scheme}&\multicolumn{2}{c|}{Protein split}\\
		&Splitting scheme&Macro AUC&Macro AUC&Micro $AUC_p$\\
		\hline
		Naive predictor&DP pairs&$0.79$&-- &--\\
		DeepDTI&Drugs&$0.88$&$0.76$&$0.70$\\
		DeepDTA&DP pairs&$0.88$&$0.77$&$0.69$\\
		DeepConv-DTI&DP pairs&$0.88$&$0.76$&$0.73$\\
		MolTrans&DP pairs&$0.90$&$0.77$&$0.74$\\
		\hline
	\end{tabular}\\

@@

\begin{itemize}
	\item \name comparison to other approaches on BioSnap prone to bias, as $ BioSnap: drugs 
	\times prots = 5500 \times 3000 $, while only 
	$\approx$ 1000 drugs have Sider Annotation, and 
\end{itemize}
